DynaProg for Scala

### 2013-01-17 docs/report/report.tex
Nits.

\documentclass[11pt]{article}
\input{inc/style.sty}
\usepackage{multicol}
\usepackage{etoolbox}

\title{DynaProg for Scala}
\subtitle{A Scala DSL for Dynamic Programming on CPU and GPU}
\begin{document}
\maketitle
\input{introduction}
\input{problems}
\input{design}
\input{implementation}
\input{benchmarks}

\section{Conclusion}
{\color{red} XXX}

\begin{verbatim}

recap of the report

recap of the results

big picture: with actual compiler technology we
Embedded DSL vs external DSL
Larger picture how to go further

\end{verbatim}

% ------------------------------------------------------------------------------------------------
\newpage
\section*{Planning}
\subsubsection*{Todo @TCK}\ul
\item Test/proof parsers are correct -- make sure implementation is correct
\item Automate test to compare against implementation
\item Benchmarks -- use CUDA profiler(?)
\item Write report
\item Port LibRNA for CUDA?
\ule

\subsubsection*{Todo @Manohar}\ul
\item Integrate LMS code generation into v4.
\item Fix Zuker coefficients
\ule

Legacy roadmap deadlines: \\
\begin{tabular}{ll}
Nov 16 & Rules normalization and automatic backtracking \\
	& GenScala on LMS + GenCuda + LMS CudaCompiler \\
Nov 23 & Problem generalization: "cyclic keyword", Zucker problem / CudaLoop optimization \\
Nov 30 &--- gap due to LMS missing knowledge --- \\
Dec 7 & Benchmarking, grammar analysis \\
Dec 14 & First thoughts for larger than device memory \\
Dec 21 & Writing report \\
Jan 4 & --- holiday --- \\
Jan 18 & Writing report: implementation description and plan for future work
\end{tabular}

\subsubsection*{Journal}
\begin{tabular}{ll}
Sep. 17	& Getting started with the project, reading related work on hash maps. \\
Sep. 24	& Parallel hashing paper solve the problem for 32bit key/value pair. Stripped CudPP. \\
		& Devised (but not implemented) extension beyond 64bit using memory areas locks. \\
---		& Change of project suggested by Vojin (supervisor): joint work with Manohar on DP \\
Oct. 01	& Problems specifications: serial/non-serial, started CUDA implementation with blocks. \\
Oct. 08	& CudAlign solves serial monadic, might adapt it (but complicated / ad-hoc / in progress). \\
		& Focus on non-serial problems that fit in GPU memory. \\
Oct. 15	& First working implementation for non-serial problems (rectangle, triangle, parallelogram) \\
Oct. 22	& No workaround for timeout, fixed by multiple kernels. Implemented backtrack on GPU. \\
Oct. 29	& Scala/C compiler engine, to use Scala/CUDA, C code must be provided. ADP (Manohar) \\
Nov. 05	& Multiple fixes and rework of ADP parsers to aim at generating C-like code. \\
Nov. 12	& Rework ADP parsers: cyclic, two-track grammars and automatic backtracking discussion. \\
Nov. 19	& Explorations LMS and Macros for C code, implementation is quite different, hence ad-hoc. \\
Nov. 26	& Full backtracking stack: apply / unapply / reapply, refactoring of the classes. \\
Dec. 03	& JNI for LibRNA to get coefficients for Zuker, errors in algebra (quite hairy code). \\
Dec. 10	& Rework concatenation operators, yield analysis, code generation. \\
Dec. 17	& Detupling, generic backtrack (vs. ad-hoc), nested aggregates, empty results support. \\
Dec. 24	& (sick 4 days), code generation: full JNI conversion support, rework CodeCompiler. \\
Dec. 31	& Writing report (design, implementation), fixing various issues, complexity analysis. \\
Jan. 7	& Writing report, attempt to fix Zuker, fix SBT, strip LibRNA. LMS C codegen (Manohar) \\
Jan. 14	& Report improvements, fixed Zuker (coherent with GAPC), {\color{red} XXX} \\
\end{tabular}

>>>>

\documentclass[11pt]{article}
\input{inc/style.sty}
\usepackage{multicol,etoolbox}

\title{DynaProg for Scala}
\subtitle{A Scala DSL for Dynamic Programming on CPU and GPU}
\begin{document}
\maketitle
\input{introduction}
\input{problems}
\input{design}
\input{implementation}
\input{benchmarks}
\input{conclusion}

% ------------------------------------------------------------------------------------------------
%\section*{Planning}
%Legacy roadmap deadlines: \\
%\begin{tabular}{ll}
%Nov 16 & Rules normalization and automatic backtracking \\
%	& GenScala on LMS + GenCuda + LMS CudaCompiler \\
%Nov 23 & Problem generalization: "cyclic keyword", Zucker problem / CudaLoop optimization \\
%Nov 30 &--- gap due to LMS missing knowledge --- \\
%Dec 7 & Benchmarking, grammar analysis \\
%Dec 14 & First thoughts for larger than device memory \\
%Dec 21 & Writing report \\
%Jan 4 & --- holiday --- \\
%Jan 18 & Writing report: implementation description and plan for future work
%\end{tabular}
%
%\subsubsection*{Journal}
%\begin{tabular}{ll}
%Sep. 17	& Getting started with the project, reading related work on hash maps. \\
%Sep. 24	& Parallel hashing paper solve the problem for 32bit key/value pair. Stripped CudPP. \\
%		& Devised (but not implemented) extension beyond 64bit using memory areas locks. \\
%---		& Change of project suggested by Vojin (supervisor): joint work with Manohar on DP \\
%Oct. 01	& Problems specifications: serial/non-serial, started CUDA implementation with blocks. \\
%Oct. 08	& CudAlign solves serial monadic, might adapt it (but complicated / ad-hoc / in progress). \\
%		& Focus on non-serial problems that fit in GPU memory. \\
%Oct. 15	& First working implementation for non-serial problems (rectangle, triangle, parallelogram) \\
%Oct. 22	& No workaround for timeout, fixed by multiple kernels. Implemented backtrack on GPU. \\
%Oct. 29	& Scala/C compiler engine, to use Scala/CUDA, C code must be provided. ADP (Manohar) \\
%Nov. 05	& Multiple fixes and rework of ADP parsers to aim at generating C-like code. \\
%Nov. 12	& Rework ADP parsers: cyclic, two-track grammars and automatic backtracking discussion. \\
%Nov. 19	& Explorations LMS and Macros for C code, implementation is quite different, hence ad-hoc. \\
%Nov. 26	& Full backtracking stack: apply / unapply / reapply, refactoring of the classes. \\
%Dec. 03	& JNI for LibRNA to get coefficients for Zuker, errors in algebra (quite hairy code). \\
%Dec. 10	& Rework concatenation operators, yield analysis, code generation. \\
%Dec. 17	& Detupling, generic backtrack (vs. ad-hoc), nested aggregates, empty results support. \\
%Dec. 24	& (sick 4 days), code generation: full JNI conversion support, rework CodeCompiler. \\
%Dec. 31	& Writing report (design, implementation), fixing various issues, complexity analysis. \\
%Jan. 7	& Writing report, attempt to fix Zuker, fix SBT, strip LibRNA. LMS C codegen (Manohar) \\
%Jan. 14	& Report improvements, fixed Zuker (coherent with GAPC), {\color{red} XXX} \\
%\end{tabular}
